Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-10-11 plos/main.tex
Make required changes.

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{lookerup.pdf}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{gambler.pdf}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.9\textwidth]{ann.pdf}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{fsm.pdf}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
        \includegraphics[width=.5\textwidth]{FSM16.pdf}
        \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{FSM16noise.pdf}
        \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{hmm.pdf}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_scores.pdf}
        \caption{\bf Scores for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_ranks.pdf}
        \caption{\bf Ranks for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_wins.pdf}
        \caption{\bf Wins for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_scores_boxplots.pdf}
        \caption{\bf Standard Tournament: Mean score per turn 
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{standard_scores_heatmap.pdf}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over 50000 tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_wins_boxplots.pdf}
        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.pdf}
        \caption{\bf Standard Tournament: rank in each tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.pdf}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_HMM\_5
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16 
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_3}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.pdf}
        \caption{\bf Noisy (5\%) Tournament: Mean score per turn
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:standard_boxplot}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{noisy_scores_heatmap.pdf}
    \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
    column players (ranked by median over
        50000 tournaments).}
    \label{fig:noisy_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.pdf}
        \caption{\bf Noisy (5\%) Tournament: number of wins per tournament
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.pdf}
        \caption{\bf Noisy (5\%) Tournament: rank in each tournament 
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.pdf}
        \caption{\bf Cooperation rates for DBS
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_1}
\end{figure}
        `
\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.pdf}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_3}
\end{figure}

>>>>

% Header and Footer with logo
\usepackage{lastpage,fancyhdr}
\usepackage[draft]{graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{lookerup.eps}
    \caption{\bf Diagrammatic representation of the Looker up Archetype.}
    \label{fig:lookerup}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.7\textwidth]{gambler.eps}
    \caption{\bf Diagrammatic representation of the Gambler Archetype.}
    \label{fig:gambler}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.9\textwidth]{ann.eps}
    \caption{\bf Diagrammatic representation of the ANN Archetype.}
    \label{fig:ann}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{fsm.eps}
    \caption{\bf Diagrammatic representation of the Finite State Machine Archetype.}
    \label{fig:fsm}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
        \includegraphics[width=.5\textwidth]{FSM16.eps}
        \caption{\bf Evolved\_FSM\_16: trained to maximize score in a standard
        tournament}
        \label{fig:fsm16}
\end{figure}

\begin{figure}
        \centering
        \includegraphics[width=.5\textwidth]{FSM16noise.eps}
        \caption{\bf Evolved\_FSM\_16\_Noise\_05: trained to maximize score in a
        noisy tournament}
        \label{fig:fsm16noise}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{hmm.eps}
    \caption{\bf Diagrammatic representation of the Hidden Markov Model Archetype.}
    \label{fig:hmm}
\end{figure}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_scores.eps}
        \caption{\bf Scores for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_scores}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_ranks.eps}
        \caption{\bf Ranks for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_ranks}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.5\textwidth]{standard_tft_wins.eps}
        \caption{\bf Wins for Tit for Tat over
        50000 tournaments.}
        \label{fig:tit_for_tat_wins}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_scores_boxplots.eps}
        \caption{\bf Standard Tournament: Mean score per turn 
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{standard_scores_heatmap.eps}
    \caption{\bf Standard Tournament: Mean score per turn of row players against
    column players (ranked by median over 50000 tournaments).}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_wins_boxplots.eps}
        \caption{\bf Standard Tournament: number of wins per tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{standard_ranks_boxplots.eps}
        \caption{\bf Standard Tournament: rank in each tournament (ranked by
        median over
        50000 tournaments).}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_EvolvedLookerUp2_2_2_array.eps}
        \caption{\bf Cooperation rates for EvolvedLookerUp\_2\_2\_2
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_1}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_HMM_5_array.eps}
        \caption{\bf Cooperation rates for Evolved\_HMM\_5
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_array.eps}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16 
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_standard_3}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_scores_boxplots.eps}
        \caption{\bf Noisy (5\%) Tournament: Mean score per turn
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{noisy_scores_heatmap.eps}
    \caption{\bf Noisy (5\%) Tournament: Mean score per turn of row players against
    column players (ranked by median over
        50000 tournaments).}
    \label{fig:noisy_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_wins_boxplots.eps}
        \caption{\bf Noisy (5\%) Tournament: number of wins per tournament
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\paperwidth]{noisy_ranks_boxplots.eps}
        \caption{\bf Noisy (5\%) Tournament: rank in each tournament 
            (strategies ordered by median score over 50000 tournaments).}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_DBS_0-75_3_4_3_5_array.eps}
        \caption{\bf Cooperation rates for DBS
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_1}
\end{figure}
        `
\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_ANN_5_Noise_05_array.eps}
        \caption{\bf Cooperation rates for Evolved\_ANN\_5\_Noise\_05
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_2}
\end{figure}

\begin{figure}[!hbtp]
        \centering
        \includegraphics[width=.7\textwidth]{cooperation_0_0_10000_Evolved_FSM_16_Noise_05_array.eps}
        \caption{\bf Cooperation rates for Evolved\_FSM\_16\_Noise\_05
            (strategies ordered by median score over 10000 tournaments).}
        \label{fig:comparison_cooperation_heatmaps_noisy_3}
\end{figure}
